### 2025-08-06 conteudo/background/codeduplication.tex
fix some ~ before ref and cite and a wrong , on tool arch

The \textit{diff} command is a command line in GNU/Linux that allows the user to compare 
two files line by line~\citep{diffcommand}. There are multiple forms in which the command 
results can be shown to the user, and Figure \ref{fig:diff} shows one of them. 
With the command results, it is easy to visualize and extract the number of lines that 
are equal and different between the two compared files.

@@

Over time, various techniques and methods have been developed in the literature
to address the code clone detection problem. For better analysis and
understanding, these approaches are categorized into five methodologies based
on their characteristics \citep{litreview}:

\begin{itemize}
    \item \textbf{Textual-based approaches:} According to Chen’s literature 
    review \citep{litreview}, this is the earliest methodology explored in 
    the field. It treats code as a text artifact and applies textual similarity
    techniques. An example is the work of~\cite{textexample}, 
    which uses parsing and grammar techniques to detect code clones.

    \item \textbf{Token-based approaches:} This method tackles the problem 
    similarly to lexical analysis in the compilation process \citep{litreview}. 
    It involves identifying programming language tokens such as constants and 
    keywords, mapping variables to independent representations, etc. An example
    is the work of~\cite{tokenexample}, which detects code 
    clones through hashed token sequences.

>>>>

The \textit{diff} command is a command line in GNU/Linux that allows the user to compare 
two files line by line~\citep{diffcommand}. There are multiple forms in which the command 
results can be shown to the user, and Figure~\ref{fig:diff} shows one of them. 
With the command results, it is easy to visualize and extract the number of lines that 
are equal and different between the two compared files.

@@

Over time, various techniques and methods have been developed in the literature
to address the code clone detection problem. For better analysis and
understanding, these approaches are categorized into five methodologies based
on their characteristics~\citep{litreview}:

\begin{itemize}
    \item \textbf{Textual-based approaches:} According to Chen’s literature 
    review~\citep{litreview}, this is the earliest methodology explored in 
    the field. It treats code as a text artifact and applies textual similarity
    techniques. An example is the work of~\cite{textexample}, 
    which uses parsing and grammar techniques to detect code clones.

    \item \textbf{Token-based approaches:} This method tackles the problem 
    similarly to lexical analysis in the compilation process~\citep{litreview}. 
    It involves identifying programming language tokens such as constants and 
    keywords, mapping variables to independent representations, etc. An example
    is the work of~\cite{tokenexample}, which detects code 
    clones through hashed token sequences.

### 2025-08-06 conteudo/results/students.tex
fix some ~ before ref and cite and a wrong , on tool arch

We asked the teaching assistant and the students who used the ArKanjo to answer a survey with 
some questions related to the tool experience, such as installation, documentation, ease of 
use, new ideas to improve the tool, etc. Appendix \ref{app:survey} has the complete survey 
with the answers.

@@

On the ArKanjo tool preprocessing step, the student reported problems of disk space usage and 
crash errors, which we knew could happen as the tool iterates and can save information about 
every pair of functions in a codebase, as we did not implement any mechanism to control the 
memory usage. The teaching assistant reported only being able to execute the preprocessor with 
the text similarity method, and the diff method kept running for hours without finishing. 
The teaching assistant's report was unexpected behavior for us, as the text similarity method 
initially looked more complex; in contrast, the \textit{diff} method is a simple counter of equal lines 
with an operation system default command. The teaching assistant report corroborates the 
gensim efficiency \citep{gensim}.

@@

The students successfully delivered the issues proposed. We found it interesting to see 
people able to contribute to the tool on the problems that we did not even know how to approach.
The issues help the user experience and facilitate other research using the ArKanjo tool that 
we may explore in future works. Appendix \ref{app:contribution} references the 
students' contributions, the issue list proposed to the students, and figures from 
the documentation webpage.

>>>>

We asked the teaching assistant and the students who used the ArKanjo to answer a survey with 
some questions related to the tool experience, such as installation, documentation, ease of 
use, new ideas to improve the tool, etc. Appendix~\ref{app:survey} has the complete survey 
with the answers.

@@

On the ArKanjo tool preprocessing step, the student reported problems of disk space usage and 
crash errors, which we knew could happen as the tool iterates and can save information about 
every pair of functions in a codebase, as we did not implement any mechanism to control the 
memory usage. The teaching assistant reported only being able to execute the preprocessor with 
the text similarity method, and the diff method kept running for hours without finishing. 
The teaching assistant's report was unexpected behavior for us, as the text similarity method 
initially looked more complex; in contrast, the \textit{diff} method is a simple counter of equal lines 
with an operation system default command. The teaching assistant report corroborates the 
gensim efficiency~\citep{gensim}.

@@

The students successfully delivered the issues proposed. We found it interesting to see 
people able to contribute to the tool on the problems that we did not even know how to approach.
The issues help the user experience and facilitate other research using the ArKanjo tool that 
we may explore in future works. Appendix~\ref{app:contribution} references the 
students' contributions, the issue list proposed to the students, and figures from 
the documentation webpage.
